---
editor_options: 
  markdown: 
    wrap: 72
---

------------------------------------------------------------------------

## Some Notes

Summarize SMP reach by repeat categories (different categories can be
collapsed into one, data can be summed)

Our deliverables: 2 tables per watershed 36 total Happy medium with
level of polish Appended to a word document, final export as pdf pdf
would be best probably

END OF THURSDAY AT THE VERY LATEST

We can at least shorten the table titles. How about: "Change in Tree
Canopy and Supporting Metrics, [Watershed_Name] Watershed and Reaches"
for the first series of tables, and "Change in Impervious Cover and
Supporting Metrics, [Watershed_Name] Watershed and Reaches" for the
second.

```{r import_packages, results='hide'}
library(data.table)
library(gtsummary)
library(kableExtra)
library(knitr)
library(readxl)
library(tidyverse)
options(scipen = 999)
```

## Read in excel file

```{r read_data}
## Import
files <- list.files(pattern = "*.xlsx", path = "data_raw/", 
                    recursive = TRUE, full.names = TRUE)
raw.data <- read_excel(files, .name_repair = "universal")
```

## Create the first table

```{r Table1}
source("R/create_table1.R")
allen <- export.table[[1]]

```

```{r maketables}

allen.table <- allen %>% 
  knitr::kable(
    caption = paste("Change in Tree Canopy and Supporting Metrics,", 
                    names(export.table[1]), "Watershed and Reaches"), 
    format = "latex",
    align = "l",
    booktabs = TRUE,
    longtable = FALSE,
    linesep = "") %>%
  kableExtra::kable_styling(
      position = "left",
      latex_options = c("striped", "repeat_header", "scale_down"),
      stripe_color = "gray!15",
      full_width = FALSE) %>%
  row_spec(row = 0, background = "#048CBD")


save_kable(allen.table, "my_latex_table.pdf", keep_tex = FALSE)
```

```{r tables2}

 kable(export.table[[1]], caption = paste0("Frequency table for the '", colnames(export.table[[1]])[2], "' variable."))

# lapply(names(individual.ROC), 
#        function(x) ggsave(filename = paste("figures/ROC_plots/ROC_plot_", 
#                                            x, ".png", sep = ""), plot = individual.ROC[[x]]))
```


